\myTitle

### 2023-10-20 author-title-etc.tex
add matt to authors.  tiny edits

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{Eric C. Anderson$^{*,\S}$, Rachel M. Giglio$^{\dagger}$, Timothy J. Smyser$^{\dagger}$}
\author{Eric C. Anderson$^{*,\S}$, Rachel M. Giglio$^{\dagger}$, Timothy J. Smyser$^{\dagger}$}

% redefine to make the affiliation list.  Note symbols are done manually
\newcommand{\myAffiliations}{$^*$Fisheries Ecology Division,
    Southwest Fisheries Science Center, National Marine Fisheries Service, NOAA,
    110 McAllister Road,
    Santa Cruz, CA 95060, USA.,
    $^\dagger$  ADDRESS FOR APHIS/NWRC}
\renewcommand{\AuthorAddresses}{\myAffiliations}

>>>>

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachel M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}
\author{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachel M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}

% redefine to make the affiliation list.  Note symbols are done manually
\newcommand{\myAffiliations}{$^*$Fisheries Ecology Division,
    Southwest Fisheries Science Center, National Marine Fisheries Service, NOAA,
    110 McAllister Road,
    Santa Cruz, CA 95060, USA.,
    $^\dagger$Dept. of Fish, Wildlife, and Conservation Biology, Colorado State University, Fort Collins, CO, USA,
    $^\ddag$Dept. of Biology, Colorado State University, Fort Collins, CO, USA,
    $^\#$National Wildlife Research Center, United States Department of Agriculture, Wildlife Services,
    Fort Collins, CO, USA
}
\renewcommand{\AuthorAddresses}{\myAffiliations}

### 2023-10-20 body-text-of-paper.tex
add matt to authors.  tiny edits

Genetic clustering algorithms are a commonly used approach to describe genetic structure among populations, reflecting the cumulative effects of isolation, connectivity (i.e., genetic migration), selection, and genetic drift.  The capacity of such algorithms to differentiate populations is limited by the extent of genetic differentiation among populations and the capacity to resolve those differences given the available marker set and sample sizes from the respective populations.  Based on an initial description of genetic structure, ecologists are frequently interested in describing patterns of genetic movement among populations, often inferred from the mismatch between the sampling location and genetic origins of a given animal \citep{paetkau1995microsatellite,wilson2003bayesian}.  Describing such patterns of movement have many implications, influencing evolutionary processes, disease dynamics \citep{huestis2019windborne}, or patterns of invasive species expansion.

>>>>

Genetic clustering algorithms are a commonly used approach to describe genetic structure among populations, reflecting the cumulative effects of isolation, connectivity (i.e., genetic migration), selection, and genetic drift.  The ability of such algorithms to differentiate populations is limited by the extent of genetic differentiation among populations and the capacity to resolve those differences given the available marker set and sample sizes from the respective populations.  Based on an initial description of genetic structure, ecologists are frequently interested in describing patterns of genetic movement among populations, often inferred from the mismatch between the sampling location and genetic origins of a given animal \citep{paetkau1995microsatellite,wilson2003bayesian}.  Describing such patterns of movement have many implications, influencing evolutionary processes, disease dynamics \citep{huestis2019windborne}, or patterns of invasive species expansion.
